Juliacon Proceedings in Quarto

### 2023-11-14 template.qmd
code: fall-back works as always, but would be nice to have support for executable code chunks

## Code

```{.julia}
println("Hello, world!")
```

>>>>

## Executable Code

Ideally, we would be able to tab into Quarto's existing support for executable, cross-referenceable code chunks.

> To create cross-referenceable code listings from executable code blocks, use `lst-label` and `lst-cap`. 
> --- [Quarto Docs](https://quarto.org/docs/prerelease/1.4/crossref.html#cross-referenceable-listings-of-executable-code-blocks)

For example, the following code block will be labeled as `lst-1` and calling `@lst-1` will render as @lst-1. This ensures that things stay up-to-date and potential errors in the code are identified early: as you render your document, the code will be executed and the output will be inserted into the document.

```{julia}
#| lst-label: lst-1
#| lst-cap: A listing caption
#| eval: false
#| echo: true

using Plots

x = -3.0:0.01:3.0
y = rand(length(x))
plot(x, y)
```

Unfortunately, I don't know how to use the special environment that is already defined for Julia in this context.

## Code Listings

The special environment that is already defined for Julia code can still be used as before.

\begin{verbatim}
\begin{lstlisting}[
    language = Julia, 
    numbers=left, 
    label={lst:exmplg}, 
    caption={Example Code Block.}
]
using Plots

x = -3.0:0.01:3.0
y = rand(length(x))
plot(x, y)
\end{lstlisting}
\end{verbatim}
\begin{lstlisting}[
    language = Julia, 
    numbers=left, 
    label={lst:exmplg}, 
    caption={Example Code Block.}
]
using Plots

x = -3.0:0.01:3.0
y = rand(length(x))
plot(x, y)
\end{lstlisting}

### 2023-11-14 template.tex
code: fall-back works as always, but would be nice to have support for executable code chunks

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{241,243,245}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.40,0.45,0.13}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.28,0.35,0.67}{#1}}
\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.00,0.46,0.62}{#1}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.07,0.07,0.07}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}

@@

\subsection{Code}\label{code}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{println}\NormalTok{(}\StringTok{"Hello, world!"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

>>>>

@@

\subsection{Executable Code}\label{executable-code}

Ideally, we would be able to tab into Quarto's existing support for
executable, cross-referenceable code chunks.

\begin{quote}
To create cross-referenceable code listings from executable code blocks,
use \texttt{lst-label} and \texttt{lst-cap}. ---
\href{https://quarto.org/docs/prerelease/1.4/crossref.html\#cross-referenceable-listings-of-executable-code-blocks}{Quarto
Docs}
\end{quote}

For example, the following code block will be labeled as \texttt{lst-1}
and calling \texttt{@lst-1} will render as Listing~\ref{lst-1}. This
ensures that things stay up-to-date and potential errors in the code are
identified early: as you render your document, the code will be executed
and the output will be inserted into the document.

\begin{codelisting}

\caption{\label{lst-1}A listing caption}

\centering{

\begin{verbatim}
using Plots

x = -3.0:0.01:3.0
y = rand(length(x))
plot(x, y)
\end{verbatim}

}

\end{codelisting}%

Unfortunately, I don't know how to use the special environment that is
already defined for Julia in this context.

\subsection{Code Listings}\label{code-listings}

The special environment that is already defined for Julia code can still
be used as before.

\begin{verbatim}
\begin{lstlisting}[
    language = Julia, 
    numbers=left, 
    label={lst:exmplg}, 
    caption={Example Code Block.}
]
using Plots

x = -3.0:0.01:3.0
y = rand(length(x))
plot(x, y)
\end{lstlisting}
\end{verbatim}
\begin{lstlisting}[
    language = Julia, 
    numbers=left, 
    label={lst:exmplg}, 
    caption={Example Code Block.}
]
using Plots

x = -3.0:0.01:3.0
y = rand(length(x))
plot(x, y)
\end{lstlisting}
